Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-08 WSSSPE1_report/WSSSPE1_summary_report.tex
adding my paper desc to community section

@@

>>>>

What are the possible career paths for a specialist software developer working as part of a scientific research group?

@@

One of the paper by Maheshwari et al~\cite{Maheshwari_WSSSPE} that was
discussed was about the role of technological catalysts in overall e-research
process.  The paper focuses on ``technology catalysts" and their role in modern
scientific research process. Technology catalyst could be defined as a role
played by an individual with a knowhow of technological advancements tasked
with user engagement with a goal of enacting scientific or engineering
applications using suitable tools and techniques to take advantage of
technological capabilities and benefitting applications.

One of the tasks of catalysts is to seek community collaborations for new
applications and user engagement thus benefitting both: science, by effective
running of scientific codes over computational infrastructure and technology,
by conducting research and seeking findings to improve technology.

The particular engagements described in the paper came up from authors work as
postdoctoral researcher at Cornell and Argonne. Interaction with the scientific
communities in both institutions resulted in these collaborations.
